Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-24 DGMM2025/paper.tex
ii visibility + merging with what i have in local

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{environ}
\usepackage{bbm}
%\usepackage{array}
%\usepackage{multirow}

@@

    \begin{figure}
        \begin{center}
            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
            \caption{Visibility of a point on an edge of a fandisk}
            \label{fig:visibility-fandisk}
        \end{center}
    \end{figure}
    \begin{figure}
        \begin{center}
            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
            \label{fig:visibility-torus-knot}
        \end{center}
    \end{figure}

@@

    \pgfplotsset{width=13cm}
    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                xlabel={Gridstep},
                ylabel={Mean distance},
                x dir=reverse,
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymax=50,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]

@@

@@

    More precisely, we choose a Gaussian function
    $\Kernel{x}:=e^{-\frac{x^2}{2\sigma^2}}$ as a weight kernel. Let
    $V_p$ be the set of visible points from the point $p$.  Let $c_p$
    be the weighted centroid of the visible points around $p$,
    i.e. $c_p := \frac{\sum_{q \in V_p} \Kernel{\|q-p\|}q}{\sum_{q \in
        V_p} \Kernel{\|q-p\|}}$.  We form the weighted covariance matrix
    $\mathcal{V}_p$ of the points $V_p$ as:
    \begin{equation}
        \mathcal{V}_p = \sum_{q \in V_p} \Kernel{\|q-p\|}(q - c_p)(q - c_p)^T.
    \end{equation}
    The \emph{visibility normal} $\vec{n}_p$ of point $p$ is defined
    as the first eigenvector of the covariance matrix $\mathcal{V}_p$
    of the visible points, corresponding to its smallest
    eigenvalue. Its orientation is chosen so as to point in the same
    direction as the average of the trivial normals to the surfels
    touching the point $p$.

    %% Let $V_p$ be the set of visible points from the point $p$. Let
    %% $c_p$ be the weighted centroid of the visible points around $p$.
    %% The normal $\vec{n}$ is defined as the first eigenvector of the
    %% covariance matrix $\mathcal{V}$ of the visible points:
    %% \begin{equation}
    %%     \mathcal{V} = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
    %% \end{equation}
    %% In order to reorient the normal, we use the trivial normal of the
    %% surface as a reference.

    \begin{figure}
        \begin{center}
            \includegraphics[width=0.8\textwidth]{pictures/torus-knot-normal-estimation}
            \caption{Normal estimation on a torus knot using the visibility
            algorithm. The normals are colored according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$
                .}
            \label{fig:normal-estimation}
        \end{center}
    \end{figure}

    \paragraph*{Experimental convergence of normal estimation.}
    [TODO] Show normal estimations along smooth shapes and compare with Integral Invariant.

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{environ}
\usepackage{bbm}

@@

    \begin{figure}
        \centering
        \begin{tabular}{c c}
            \includegraphics[width=0.4\textwidth]{pictures/visibility_from_given_point_r_10} &
            \includegraphics[width=0.4\textwidth]{pictures/visibility_aware_of_features}
        \end{tabular}
        \caption{Examples of visibility on a fandisk and a torus knot. First one is on the edge
        of a fandisk, where the visibility stops at the edges. The other one is in the interior
        of a torus knot, where we can see that the visibility is feature-aware and doesn't see
        the other side of the torus' branch.}
        \label{fig:visibility-examples}
    \end{figure}
%
%    \begin{figure}
%        \begin{center}
%            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
%            \caption{Visibility of a point on an edge of a fandisk}
%            \label{fig:visibility-fandisk}
%        \end{center}
%    \end{figure}
%    \begin{figure}
%        \begin{center}
%            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
%            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
%            \label{fig:visibility-torus-knot}
%        \end{center}
%    \end{figure}

@@

    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                width=0.8\textwidth,
                legend columns=3,
                xlabel={Gridstep},
                ylabel={Mean distance},
                x dir=reverse,
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymax=50,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]

@@

                width=0.8\textwidth,

@@

    More precisely, we choose a Gaussian function
    $\Kernel{x}\coloneqq e^{-\frac{x^2}{2\sigma^2}}$ as a weight kernel. Let
    $V_p$ be the set of visible points from the point $p$.  Let $c_p$
    be the weighted centroid of the visible points around $p$,
    i.e. $c_p \coloneqq \frac{\sum_{q \in V_p} \Kernel{\|q-p\|}q}{\sum_{q \in
        V_p} \Kernel{\|q-p\|}}$.  We form the weighted covariance matrix
    $\mathcal{V}_p$ of the points $V_p$ as:
    \begin{equation}
        \mathcal{V}_p = \sum_{q \in V_p} \Kernel{\|q-p\|}(q - c_p)(q - c_p)^T.
    \end{equation}
    The \emph{visibility normal} $\vec{n}_p$ of point $p$ is defined
    as the first eigenvector of the covariance matrix $\mathcal{V}_p$
    of the visible points, corresponding to its smallest
    eigenvalue. Its orientation is chosen so as to point in the same
    direction as the average of the trivial normals to the surfels
    touching the point $p$. \ref{fig:normals-estimation} shows an example
    of our normals compared to normals computed with II

    \begin{figure}
        \centering
        \begin{tabular}{|c||c|c|}
            \hline
            II normals &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
            \hline
            Visibility normals &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
            \hline
        \end{tabular}
        \caption{Examples of normals computed on a chinese dragon as a color map. First set displays II normals, second set uses the visibility
        algorithm to compute them. The normals are colored according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$
            . The right images are the smooth version of the left images}
        \label{fig:normals-estimation}
    \end{figure}

    Then, to compute the curvatures, we use the Corrected Normal Current
    estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
    above.
